---
title: "MarketBasketAnalysisWith_R"
output: pdf_document
date: "`r Sys.Date()`"
---
a.Load the required libraries: rules and arulesViz.
b.Load the dataset named " Income" (either provided in or from an external source).
```{r}
#load the required libraries
library(arules)
library(arulesViz)
#load the data
data("Income")
#inspect the data
str(Income)

```
c. Dataset in transaction for Market Basket Analysis.
```{r}
library(arules)
library(arulesViz)
inspect(Income)
```
d.Use the apriori algorithm to mine association rules
```{r}
#Use the apriori algorithm to mine association rules
income_rules <- apriori(Income, parameter = list(support = 0.5, confidence = 0.5))
```
e. Fine-tune the parameters such as support and confidence levels to obtain meaningful rules.
```{r}
# support 0.1 and confidence0.8 
#At least 10% of the transactions should contain the items in the rule
#At least 80% of the transactions containing the antecedent should also contain the consequent

income_rules <- apriori(Income, parameter = list(support = 0.1, confidence = 0.8))

```
f. Inspect and analyze the generated rules.
```{r}
```{r}
#Inspect and analyze the generated rules.
inspect(income_rules)


```

g. Sort the rules based on support, confidence, and lift.

```{r}
#Sort the rules based on support, confidence, and lift
income_rules <- sort(income_rules, by = "lift")
inspect(income_rules)


```

```{r}
#sort the rules based on confidence
income_rules <- sort(income_rules, by = "confidence")
inspect(income_rules)
```

```{r}
#sort the rules based on support
income_rules <- sort(income_rules, by = "support")
inspect(income_rules)
```
h. Identify and remove redundant rules.
```{r}
#Identify and remove redundant rules.
income_rules <- income_rules[!duplicated(income_rules)]
```

i. Visualize the association rules using plot function and ensure interactivity.
```{r}
#Visualize the association rules using plot function and ensure interactivity
plot(income_rules, method = "graph", control = list(type = "items"))
```

